---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Homework 6 R Package: Sparse Numeric Vector Class and Methods
<!-- badges: start -->
[![R-CMD-check](https://github.com/DanaNguyen18/sparseMethods/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/DanaNguyen18/sparseMethods/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

# Description

`sparseMethods` provides an S4 class, `sparse_numeric`, for efficiently storing 
numeric vectors by keeping only the nonzero entries and their positions. 

The package implements:

- Custom S4 class `sparse_numeric` for sparse vectors (`value`, `pos`, `length`)
- Arithmetic on sparse vectors: `+`, `-`, `*`
- Sparse functions: `sparse_add()`, `sparse_sub()`, `sparse_mult()`, `sparse_crossprod()`
- Vector summaries: `mean()`, `norm()`, `standardize()`
- Visualization with `plot()`
- Custom printing via `show()`
- Full reference documentation generated using **roxygen2**
- Automated testing framework using **testthat**
- A **pkgdown** website for easy navigation and examples

This package successfully passes **R CMD check** with  0 errors, 0 warnings, and 0 notes and achieves 95% test coverage.


# Installation

You can install the development version of **sparseMethods** from GitHub using:

```{r}
# install.packages("devtools")
devtools::install_github("DanaNguyen18/sparseMethods")

```


## Example

This is a basic example showing you the methods. 
```{r}
library(sparseMethods)

# Create sparse vectors
x <- as(c(1, 0, 3, 0, 5), "sparse_numeric")
y <- as(c(0, 4, 0, 2, 1), "sparse_numeric")

# Print the sparse vectors
x
y

# Arithmetic
x + y
x - y
x * y

# Cross product (dot product)
sparse_crossprod(x, y)

# Means and norms
mean(x)
norm(x)

# Standardization
standardize(x)

# Plot
plot(x, y)

# Show
show(x)

```

# PkgDown Website and License

The pkgDown website can be accessed at: http://dananguyen18.github.io/sparseMethods/

This package is released under the MIT license. 
