---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sparseMethods
<!-- badges: start -->
[![R-CMD-check](https://github.com/DanaNguyen18/sparseMethods/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/DanaNguyen18/sparseMethods/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->



# Description
sparseMethods provides an S4 class, sparse_numeric, for storing numeric
vectors by keeping only the nonzero entries and their positions, sparse vectors.
The package implements:

Arithmetic on sparse vectors: +, -, *

Sparse functions:
sparse_add(),
sparse_sub(),
sparse_mult(),
sparse_crossprod(),

Vector summaries:
mean(),
norm(),
standardize(),

Visualization with plot(),
Custom printing via show()

This package demonstrates how to define S4 classes, generics, and methods in R.

# Installation
You can install the development version of sparseMethods from GitHub using:


# install.packages("devtools")
devtools::install_github("DanaNguyen18/sparseMethods")

## Example

This is a basic example showing you the methods. 

```{r example}
library(sparseMethods)

# Create sparse vectors
x <- as(c(1, 0, 3, 0, 5), "sparse_numeric")
y <- as(c(0, 4, 0, 2, 1), "sparse_numeric")

# Print the sparse vectors
x
y

# Arithmetic
x + y
x - y
x * y

# Cross product (dot product)
sparse_crossprod(x, y)

# Means and norms
mean(x)
norm(x)

# Standardization
standardize(x)

# Plot
plot(x, y)

#Show
show(x)
```

